---
title: "paretoportatil005"
author: "Diego Serrano Ortega"
date: "2023-06-13"
output: html_document
---
---
title: "Simulación California"
author: "Diego Serrano Ortega"
date: "2023-04-18"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(refund)
```





Perform cross-validation for choosing N1, degree of Bernstein polynomial.

```{r, tidy = FALSE,message=FALSE,warning=FALSE, fig.width=5, fig.height=5,echo=FALSE}
#@N1: Degree of Bernstein polynomial basis.
#@y: Scalar response.
#@X: Functional covariate on a grid, n * m matrix.
#T: Equispaced time-grid of functional observations.
#constr: Constraints, one of positive,negative,inc (increasing), dec (decreasing), convex, concave.
SOFR.con<-function(N1,y,X,T,n2=m,constr="positive"){
  m<-length(T)
  tpred<-seq(0,1,l=n2)
  X1 <- NULL
  for(k in 0:N1){
    X1 <- cbind(X1, dbeta(T, shape1=(k+1), shape2=N1-k+1))
  }
  
  W<-matrix(0,N,(N1+1))
  for(i in 1:N)
  {for (k in 1:ncol(X1))
  {
    W[i,k]<-mean(X[i,]*X1[,k])
  }
  }
  
  library(restriktor)
  glmod<-lm(y~W)
  summary(glmod)
  if(constr=="positive"){
    A1<-diag(ncol(X1))
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  
  if(constr=="negative"){
    A1<--diag(ncol(X1))
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  
  if(constr=="dec"){
    A1<-matrix(0,nrow=N1,ncol=(N1+1),byrow = TRUE)
    for(i in 1:(N1))
    {A1[i,i]=1
    A1[i,(i+1)]=-1}
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  if(constr=="inc"){
    A1<-matrix(0,nrow=N1,ncol=(N1+1),byrow = TRUE)
    for(i in 1:(N1))
    {A1[i,i]=-1
    A1[i,(i+1)]=1}
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  
  if(constr=="convex"){
    A1<-matrix(0,nrow=(N1-1),ncol=(N1+1),byrow = TRUE)
    for(i in 1:(N1-1))
    {A1[i,i]=1
    A1[i,i+1]=-2
    A1[i,i+2]=1
    }
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  
  if(constr=="concave"){
    A1<-matrix(0,nrow=(N1-1),ncol=(N1+1),byrow = TRUE)
    for(i in 1:(N1-1))
    {A1[i,i]=-1
    A1[i,i+1]=2
    A1[i,i+2]=-1
    }
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
  }
  
  fit.con <- restriktor(glmod, constraints = A,rhs=b,neq=0)
  betares<- coef(fit.con) 
  ypred<-fit.con$fitted
  
  beta1est<-function(x){
    
    n<-length(x)
    X1 <- NULL
    for(k in 0:N1){
      X1 <- cbind(X1, dbeta(x, shape1=(k+1), shape2=N1-k+1))
    }
    pred<-as.numeric(X1%*%betares[-1])
    pred
  }
  coef <- beta1est(tpred)
  betaresun<-coef(glmod)
  Wreal<-cbind(rep(1,N),W)
  Omegahat<-(t(Wreal)%*%Wreal)*(1/N)
  ###sigmahat beta ur###
  sigmahat_ur<-as.matrix(vcov(glmod))
  L_omega<-t(chol(Omegahat))
  library(MASS)
  zgen<-function(...)
  {betacan_ur<-mvrnorm(n=1,mu=betaresun,Sigma=sigmahat_ur)
  Ystar<-as.numeric(L_omega%*%(betacan_ur))
  Xstar<-L_omega
  library(quadprog)
  #ATb> b0.
  Dmat = t(Xstar) %*% Xstar
  Amat = t(A) 
  bvec = b
  dvec = t(Xstar) %*% Ystar
  out<-solve.QP(Dmat = Dmat, dvec = dvec, Amat = Amat, bvec = bvec, meq = 0, factorized = F)
  betaproj<-out$solution #out$solution
  betaproj  
  }
  betagenmat<-sapply(1:10000,zgen)##10000 simulations from d
  betagenmat<-t(betagenmat)
  
  bootmatest<-matrix(0,10000,m)
  for(b in 1:10000){
    betatemp<-betagenmat[b,]
    beta1estboot<-function(x){
      
      n<-length(x)
      X1 <- NULL
      for(k in 0:N1){
        X1 <- cbind(X1, dbeta(x, shape1=(k+1), shape2=N1-k+1))
      }
      pred<-as.numeric(X1%*%betatemp[-1])
      pred
    }
    bootmatest[b,]<-beta1estboot(T)
  }
  lb<-apply(bootmatest,2, quantile,probs=0.025)
  ub<-apply(bootmatest,2, quantile,probs=0.975)
  result<-list(betaSOFR=coef,yhat=ypred,lb=lb,ub=ub)
  return(result)
  }
 
```


```{r, tidy = FALSE,message=FALSE,warning=FALSE, fig.width=5, fig.height=5, echo = FALSE}
#@N1: Degree of Bernstein polynomial basis.
#@y: Scalar response.
#@X: Functional covariate on a grid, n * m matrix.
#T: Equispaced time-grid of functional observations.
#constr: Constraints, one of positive,negative,inc (increasing), dec (decreasing), convex, concave.
############CV function FOR CHOOSING N, degree of BP##################
  cv.SOFR.con<-function(N1,y,X,T,constr="positive")
  { n<-length(y)
    library(caret)
    set.seed(1)
    find<-createFolds(y=c(1:n), k = 5, list = FALSE, returnTrain = FALSE)
    cvscore<-c()
    for (v in 1:5)
    {tempind=which(find==v)
    X1 <- NULL
    for(k in 0:N1){
      X1 <- cbind(X1, dbeta(T, shape1=(k+1), shape2=N1-k+1))
    }
    nte<-length(tempind)
    ntr<-n-nte
    W<-matrix(0,N,(N1+1))
    for(i in 1:n)
    {for (k in 1:ncol(X1))
    {
      W[i,k]<-mean(X[i,]*X1[,k])
    }
    }
    
    Wtr<-W[-tempind,]
    Wte<-W[tempind,]
    ytr<-y[-tempind]
    yte<-y[tempind]
    
    library(restriktor)
    glmod<-lm(ytr~Wtr)
    summary(glmod)
    
    if(constr=="positive"){
    A1<-diag(ncol(X1))
    A<-cbind(rep(0,nrow(A1)),A1)
    b=rep(0,nrow(A))
    }
    
    if(constr=="negative"){
      A1<--diag(ncol(X1))
      A<-cbind(rep(0,nrow(A1)),A1)
      b=rep(0,nrow(A))
    }
    
    if(constr=="dec"){
      A1<-matrix(0,nrow=N1,ncol=(N1+1),byrow = TRUE)
      for(i in 1:(N1))
      {A1[i,i]=1
      A1[i,(i+1)]=-1}
      A<-cbind(rep(0,nrow(A1)),A1)
      b=rep(0,nrow(A))
    }
    if(constr=="inc"){
      A1<-matrix(0,nrow=N1,ncol=(N1+1),byrow = TRUE)
      for(i in 1:(N1))
      {A1[i,i]=-1
      A1[i,(i+1)]=1}
      A<-cbind(rep(0,nrow(A1)),A1)
      b=rep(0,nrow(A))
    }
    
    if(constr=="convex"){
      A1<-matrix(0,nrow=(N1-1),ncol=(N1+1),byrow = TRUE)
      for(i in 1:(N1-1))
      {A1[i,i]=1
      A1[i,i+1]=-2
      A1[i,i+2]=1
      }
      A<-cbind(rep(0,nrow(A1)),A1)
      b=rep(0,nrow(A))
    }
    
    if(constr=="concave"){
      A1<-matrix(0,nrow=(N1-1),ncol=(N1+1),byrow = TRUE)
      for(i in 1:(N1-1))
      {A1[i,i]=-1
      A1[i,i+1]=2
      A1[i,i+2]=-1
      }
      A<-cbind(rep(0,nrow(A1)),A1)
      b=rep(0,nrow(A))
    }
    
    fit.con <- restriktor(glmod, constraints = A,rhs=b,neq=0)
    betares<- coef(fit.con) 
    Xtemat<-cbind(rep(1,nte),Wte)
    ypred<-as.numeric(Xtemat%*%betares)
    cvscore[v]<- mean((yte-ypred)^2)
    }
    cverror<-mean(cvscore)
    return(cverror)
  }
  cv.SOFR.con<-Vectorize(cv.SOFR.con,vectorize.args = "N1")
  
```


Function for *UNCONSTRAINED* estimation. It is a modified version of SOFR.con in which I removed the constraints. This way the unconstrained beta coefficient is fitted using the same R functions than its constrained counterpart. I did not run cross validation to find the degree of the Bernstein polynomial, I just picked 4 as they say in the paper to speed up the process.  

```{r, tidy = FALSE,message=FALSE,warning=FALSE, fig.width=5, fig.height=5, echo=FALSE}
#@N1: Degree of Bernstein polynomial basis.
#@y: Scalar response.
#@X: Functional covariate on a grid, n * m matrix.
#T: Equispaced time-grid of functional observations.
#constr: Constraints, one of positive,negative,inc (increasing), dec (decreasing), convex, concave.
SOFR.NULL<-function(N1,y,X,T,n2=m,constr=NULL){
  m<-length(T)
  tpred<-seq(0,1,l=n2)
  X1 <- NULL
  for(k in 0:N1){
    X1 <- cbind(X1, dbeta(T, shape1=(k+1), shape2=N1-k+1))
  }
  
  W<-matrix(0,N,(N1+1))
  for(i in 1:N)
  {for (k in 1:ncol(X1))
  {
    W[i,k]<-mean(X[i,]*X1[,k])
  }
  }
  
  library(restriktor)
  glmod<-lm(y~W)
  summary(glmod)
  
  fit.con <- restriktor(glmod, constraints = NULL, rhs=NULL,neq=0)
  betares<- coef(fit.con) 
  ypred<-fit.con$fitted
  
  beta1est<-function(x){
    
    n<-length(x)
    X1 <- NULL
    for(k in 0:N1){
      X1 <- cbind(X1, dbeta(x, shape1=(k+1), shape2=N1-k+1))
    }
    pred<-as.numeric(X1%*%betares[-1])
    pred
  }
  coef <- beta1est(tpred)
  betaresun<-coef(glmod)
  Wreal<-cbind(rep(1,N),W)
  Omegahat<-(t(Wreal)%*%Wreal)*(1/N)
  
  result<-list(betaSOFR=coef, yhat=ypred)
  return(result)
  }
 
```
























```{r, echo=FALSE}
#beta se genera a partir de la densidad de una normal estándar
m=50
T<- seq(0.05, 1, length = m)
T2<- seq(0.05, 1, length = 501)
betaT<-pareto_pdf(T, b =0.1, loc=-0.4, scale=1)
betaT2<-pareto_pdf(T2, b =0.1, loc=-0.4, scale=1)
#Limits
n=length(betaT)-1
a = 0
b = 1
#Step of the grid. Recall that n is the number of subintervals.
h = (b-a)/n

#Nodes
#nodes = seq(a, b, h)

#note for myself: n is the number of subintervals, n+1 number of nodes

#weights. 1/3 for the limits, 2/3 for the odd subintervals, 4/3 for the even ones. 
w = rep(1, n+1)
w[seq(2, n, 2)] = 4/3
w[seq(3, n, 2)] = 2/3
w[1] = w[n+1] = 1/3

W=diag(w)
```


#SIMULATIONS TO CALCULATE IMSE AND MSE

```{r, cache=TRUE}
set.seed(1)
m = 50
n_sims = 200
T<- seq(0.05, 1, length = m)
T2<- seq(0.05, 1, length = 501)

#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}


betaT<-pareto_pdf(T, b =0.1, loc=-0.4, scale=1)
betaT2 <-pareto_pdf(T2, b =0.1, loc=-0.4, scale=1)
#Limits

# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_uncons=rep(0, n_sims)
MSE_uncons=rep(0, n_sims)


tiempo_unconstrained=0

rankX <- 20





Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0

write.matrix(betaT,file="betaT_dec.csv", sep=",")
write.matrix(betaT2,file="betaT2_dec.csv", sep=",")

start_time= Sys.time()
for (N in c(35,75,125)){
for (i in 1:n_sims) {
  ###########Generating data##############################
  eps<-rnorm(N,0,0.01)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  

  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T,constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1

  

  out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t = out.NULL$betaSOFR

  yhat=out.NULL$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_uncons[i] = mean((y-yhat)**2)




IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
MSE_uncons[i] = mean((y-yhat)**2)
end_time= Sys.time()

}
tiempo_unconstrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.975))
#
## Combine results into a data frame
results_unconstrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)


print(paste0('IMSE for N=',N, ':', mean(IMSE_uncons)*1000))
print(paste0('MSE for N=',N, ':', mean(MSE_uncons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, ':', sd(IMSE_uncons)))
print(paste0('Standard deviation of the MSE for N=',N, ':', sd(MSE_uncons)))
print(paste0('Times:', tiempo_unconstrained))
}
```




```{r, cache=TRUE}
set.seed(1)
m = 50
n_sims = 200
T<- seq(0.05, 1, length = m)
T2<- seq(0.05, 1, length = 501)

#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}


betaT<-pareto_pdf(T, b =0.1, loc=-0.4, scale=1)
betaT2 <-pareto_pdf(T2, b =0.1, loc=-0.4, scale=1)
#Limits

# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_uncons=rep(0, n_sims)
MSE_uncons=rep(0, n_sims)


tiempo_unconstrained=0

rankX <- 20





Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0

write.matrix(betaT,file="betaT_dec.csv", sep=",")
write.matrix(betaT2,file="betaT2_dec.csv", sep=",")

start_time= Sys.time()
for (N in c(125)){
for (i in 1:n_sims) {
  ###########Generating data##############################
  eps<-rnorm(N,0,0.01)
print(i)


  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  

  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T, constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1

  

  out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t = out.NULL$betaSOFR

  yhat=out.NULL$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_uncons[i] = mean((y-yhat)**2)



IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
MSE_uncons[i] = mean((y-yhat)**2)
end_time= Sys.time()

}
tiempo_unconstrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.975))
#
## Combine results into a data frame
results_unconstrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)


print(paste0('IMSE for N=',N, ':', mean(IMSE_uncons)*1000))
print(paste0('MSE for N=',N, ':', mean(MSE_uncons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, ':', sd(IMSE_uncons)))
print(paste0('Standard deviation of the MSE for N=',N, ':', sd(MSE_uncons)))
print(paste0('Times:', tiempo_unconstrained))
}
```




# CONSTRAINED

### PLOTS




```{r}
# set.seed(1)
# m = 100
# n_sims = 1
# # Initialize matrix to store fitted values
# fitted_means_matrix <- matrix(0, n_sims, m)
# fitted_lower_matrix <- matrix(0, n_sims, m)
# fitted_upper_matrix <- matrix(0, n_sims, m)
# T<- seq(0.1, 20, length = m)
# eps<-rnorm(N,0,0.05)
# #beta se genera a partir de la densidad de una normal estándar
# betaT=pareto_pdf(T, b =1, loc=-0.9, scale=1)
# 
# IMSE_cons=rep(0, n_sims)
# MSE_cons=rep(0, n_sims)
# 
# tiempo_constrained=0
# alpha <- 0.15
# rankX <- 8
# Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
# lambda <- rankX:1
# 
# for (i in 1:n_sims) {
#   
#   ###########Generating data##############################
#   
#   eps<-rnorm(N,0,0.05)
#   #beta se genera a partir de la densidad de una normal estándar
# 
# 
#   # He simplificado las X
# 
#   Xi <- sapply(lambda, function(l)
#     scale(rnorm(N, sd=sqrt(l)), scale=FALSE))
#   
#   X <- Xi %*% t(Phi) 
# 
#   lfterm<-as.numeric((1/m)*X%*%betaT)
#   y<-alpha+lfterm+eps
#   n<-length(y)
#   m<-length(T)
#  
#   
#   N1=3
#   #######################CHOOSE N1#######################
#   
#   #cv.SOFR.con<-Vectorize(cv.SOFR.con,vectorize.args = "N1")
#   #Ngrid<-c(3:8)  ###grid for choosing N1
#   #cv<-cv.SOFR.con(Ngrid,y,X,T,constr = "positive")
#   #indmin<-which.min(cv)  
# #
#   #N1=Ngrid[indmin] #selected N1
#   
#   ############################################
#   
#   out<-SOFR.con(N1,y,X,T,m,constr = "positive")
#   beta1t<-out$betaSOFR #constrained estimate
#   lb<-out$lb ##projection based confidence intervals
#   ub<-out$ub 
#   plot(T,betaT)
#   lines(T,beta1t)
# }
```




```{r}
set.seed(1)

for (N in c(35, 75, 125)){
start_time= Sys.time()
for (i in 1:n_sims) {
  
  ###########Generating data##############################
  
  eps<-rnorm(N,0,0.01)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  
  write.matrix(X,file=paste("X_dec001_", i,"_", N, ".csv", sep=""), sep= ",")

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  
  write.matrix(y,file=paste("y_dec001_", i,"_", N, ".csv", sep=""), sep= ",")
}
}
```





### Cálculo del IMSE y el MSE





```{r, cache=TRUE}
set.seed(1)
m = 50
n_sims = 200
# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_cons=rep(0, n_sims)
MSE_cons=rep(0, n_sims)


tiempo_constrained=0

rankX <- 20

library(MASS)

#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}

Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0



for (N in c(35, 75, 125)){
start_time= Sys.time()
for (i in 1:n_sims) {
  
  ###########Generating data##############################
  
  eps<-rnorm(N,0,0.01)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  
  write.matrix(X,file=paste("X_dec_", i,"_", N, ".csv", sep=""), sep= ",")

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  
  write.matrix(y,file=paste("y_dec_", i,"_", N, ".csv", sep=""), sep= ",")
  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T,constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1

  
  out<-SOFR.con(N1,y,X,T,m,constr = "dec")
  # out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t<-out$betaSOFR #constrained estimate

  yhat=out$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_cons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_cons[i] = mean((y-yhat)**2)
  
}
end_time= Sys.time()
tiempo_constrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.975))

# Combine results into a data frame
results_constrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)

print(paste0('IMSE for N=',N, mean(IMSE_cons)*1000))
print(paste0('MSE for N=',N, mean(MSE_cons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, sd(IMSE_cons)))
print(paste0('Standard deviation of the MSE for N=',N, sd(MSE_cons)))
print(paste0('Times:', tiempo_constrained))
}
```



```{r}
print(MSE_uncons*1000)
print(IMSE_uncons*1000)
print(MSE_cons*1000)
print(IMSE_cons*1000)
```



```{r, fig.width=5.5, fig.height=4.5}
#par(mfrow=c(1,2))
#
#  plot(T, betaT, col='#666E86', ylim=c(-0.05,1.5), type='l') #true coefficient function
#  lines(T,results_constrained$mean,col="#5F3108",lty=5) #unconstrained estimate
#  lines(T,results_constrained$lower,col="#B99B81",lty=3) #projection based C.I
#  lines(T,results_constrained$upper,col="#B99B81",lty=3)  #projection based C.I
#  abline(h=0, col='#780000')
#
#  plot(T,betaT, col='#666E86', ylim=c(-0.05,1.5), type='l') #true coefficient function
#  lines(T,results_unconstrained$mean,col="#5F3108",lty=5) #unconstrained estimate
#  lines(T,results_unconstrained$lower,col="#B99B81",lty=3) #projection based C.I
#  lines(T,results_unconstrained$upper,col="#B99B81",lty=3)  #projection based C.I
#  abline(h=0, col='#780000')
#  
```



```{r, fig.width=2.75, fig.height=3.5}
library(ggplot2)
library(gridExtra)
# Create a data frame with the values for T, betaT, and the results
df <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_unconstrained$mean,
                 lower = results_unconstrained$lower,
                 upper = results_unconstrained$upper)

df2 <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_constrained$mean,
                 lower = results_constrained$lower,
                 upper = results_constrained$upper)

# Create the plot using ggplot


# Create a data frame with the values for T, betaT, and the results


# Create the plot using ggplot
ggplot(df, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = lower), color = "#B99B81",linetype= "dashed", linewidth=0.25)+
  geom_line(aes(y = upper),color = "#B99B81", linetype="dashed",  linewidth=0.25)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 
# Create a data frame with the values for T, betaT, and the results


# Create the plot using ggplot
ggplot(df2, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = lower), color = "#B99B81",linetype= "dashed", size=1)+
  geom_line(aes(y = upper),color = "#B99B81", linetype="dashed", size=1)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 



#legend(0.80,95000, box.col="white", cex=1.5, c(expression(paste("MWW P-value = 1.4 * ", 10^-16))))

```











```{r, fig.width=2.75, fig.height=3.5}
library(ggplot2)
library(gridExtra)
# Create a data frame with the values for T, betaT, and the results
df <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_unconstrained$mean,
                 lower = results_unconstrained$lower,
                 upper = results_unconstrained$upper)

df2 <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_constrained$mean,
                 lower = results_constrained$lower,
                 upper = results_constrained$upper)

# Create the plot using ggplot


# Create a data frame with the values for T, betaT, and the results


# Create the plot using ggplot
ggplot(df, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = 0.001+lower), color = "#B99B81",linetype= "dashed", linewidth=1)+
  geom_line(aes(y = -0.002+upper),color = "#B99B81", linetype="dashed",  linewidth=1)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 
# Create a data frame with the values for T, betaT, and the results


# Create the plot using ggplot
ggplot(df2, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = lower), color = "#B99B81",linetype= "dashed", size=1)+
  geom_line(aes(y = upper),color = "#B99B81", linetype="dashed", size=1)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 



#legend(0.80,95000, box.col="white", cex=1.5, c(expression(paste("MWW P-value = 1.4 * ", 10^-16))))

```




































































































```{r, echo=FALSE}
#beta se genera a partir de la densidad de una normal estándar
m=50

#Limits
n=length(betaT)-1
a = 0
b = 1
#Step of the grid. Recall that n is the number of subintervals.
h = (b-a)/n

#Nodes
#nodes = seq(a, b, h)

#note for myself: n is the number of subintervals, n+1 number of nodes

#weights. 1/3 for the limits, 2/3 for the odd subintervals, 4/3 for the even ones. 
w = rep(1, n+1)
w[seq(2, n, 2)] = 4/3
w[seq(3, n, 2)] = 2/3
w[1] = w[n+1] = 1/3

W=diag(w)
```




AAAAAAAAAAAAAAAAAAAAAAAA







```{r, cache=TRUE}
set.seed(1)

#Limits

# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_uncons=rep(0, n_sims)
MSE_uncons=rep(0, n_sims)


tiempo_unconstrained=0

rankX <- 20



#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}

Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0



start_time= Sys.time()
for (N in c(125)){
for (i in 1:n_sims) {
  ###########Generating data##############################

  eps<-rnorm(N,0,0.05)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  

  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T, constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1

  

  out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t = out.NULL$betaSOFR

  
  yhat=out.NULL$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_uncons[i] = mean((y-yhat)**2)

end_time= Sys.time()

}
tiempo_unconstrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.975))
#
## Combine results into a data frame
results_unconstrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)


print(paste0('IMSE for N=',N, ':', mean(IMSE_uncons)*1000))
print(paste0('MSE for N=',N, ':', mean(MSE_uncons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, ':', sd(IMSE_uncons)))
print(paste0('Standard deviation of the MSE for N=',N, ':', sd(MSE_uncons)))
print(paste0('Times:', tiempo_unconstrained))
}
```


```{r}
print(IMSE_uncons*1000)
```





AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA

#SIMULATIONS TO CALCULATE IMSE AND MSE

```{r, cache=TRUE}
set.seed(1)

#Limits

# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_uncons=rep(0, n_sims)
MSE_uncons=rep(0, n_sims)


tiempo_unconstrained=0

rankX <- 20



#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}

Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0



start_time= Sys.time()
for (N in c(125)){
for (i in 1:n_sims) {
  ###########Generating data##############################
  print(i)
  eps<-rnorm(N,0,0.05)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  

  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T, constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1
  plot(T,betaT)
  plot(T,beta1t)
  

  out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t = out.NULL$betaSOFR

  yhat=out.NULL$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_uncons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_uncons[i] = mean((y-yhat)**2)


end_time= Sys.time()

}
tiempo_unconstrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_vals_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_vals_matrix, 2, function(x) quantile(x, 0.975))
#
## Combine results into a data frame
results_unconstrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)


print(paste0('IMSE for N=',N, ':', mean(IMSE_uncons)*1000))
print(paste0('MSE for N=',N, ':', mean(MSE_uncons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, ':', sd(IMSE_uncons)))
print(paste0('Standard deviation of the MSE for N=',N, ':', sd(MSE_uncons)))
print(paste0('Times:', tiempo_unconstrained))
}
```







# CONSTRAINED

### PLOTS




```{r}
# set.seed(1)
# m = 100
# n_sims = 1
# # Initialize matrix to store fitted values
# fitted_means_matrix <- matrix(0, n_sims, m)
# fitted_lower_matrix <- matrix(0, n_sims, m)
# fitted_upper_matrix <- matrix(0, n_sims, m)
# T<- seq(0.1, 20, length = m)
# eps<-rnorm(N,0,0.05)
# #beta se genera a partir de la densidad de una normal estándar
# betaT=pareto_pdf(T, b =1, loc=-0.9, scale=1)
# 
# IMSE_cons=rep(0, n_sims)
# MSE_cons=rep(0, n_sims)
# 
# tiempo_constrained=0
# alpha <- 0.15
# rankX <- 8
# Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
# lambda <- rankX:1
# 
# for (i in 1:n_sims) {
#   
#   ###########Generating data##############################
#   
#   eps<-rnorm(N,0,0.05)
#   #beta se genera a partir de la densidad de una normal estándar
# 
# 
#   # He simplificado las X
# 
#   Xi <- sapply(lambda, function(l)
#     scale(rnorm(N, sd=sqrt(l)), scale=FALSE))
#   
#   X <- Xi %*% t(Phi) 
# 
#   lfterm<-as.numeric((1/m)*X%*%betaT)
#   y<-alpha+lfterm+eps
#   n<-length(y)
#   m<-length(T)
#  
#   
#   N1=3
#   #######################CHOOSE N1#######################
#   
#   #cv.SOFR.con<-Vectorize(cv.SOFR.con,vectorize.args = "N1")
#   #Ngrid<-c(3:8)  ###grid for choosing N1
#   #cv<-cv.SOFR.con(Ngrid,y,X,T,constr = "positive")
#   #indmin<-which.min(cv)  
# #
#   #N1=Ngrid[indmin] #selected N1
#   
#   ############################################
#   
#   out<-SOFR.con(N1,y,X,T,m,constr = "positive")
#   beta1t<-out$betaSOFR #constrained estimate
#   lb<-out$lb ##projection based confidence intervals
#   ub<-out$ub 
#   plot(T,betaT)
#   lines(T,beta1t)
# }
```








### Cálculo del IMSE y el MSE





```{r, cache=TRUE}
set.seed(1)
m = 50
n_sims = 200
# Initialize matrix to store fitted values
fitted_means_matrix <- matrix(0, n_sims, m)
fitted_lower_matrix <- matrix(0, n_sims, m)
fitted_upper_matrix <- matrix(0, n_sims, m)



IMSE_cons=rep(0, n_sims)
MSE_cons=rep(0, n_sims)


tiempo_constrained=0

rankX <- 20

library(MASS)

#beta se genera a partir de la densidad de Pareto
pareto_pdf <- function(x, b = 1, scale = 1, loc = 1){
  density <- b / ((x-loc)/scale)^(b + 1)
  return(density)}

Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
lambda <- rankX:1
cont=0



for (N in c(35, 75, 125)){
start_time= Sys.time()
for (i in 1:n_sims) {
  
  ###########Generating data##############################
  
  eps<-rnorm(N,0,0.05)



  Phi <- cbind(1/sqrt(m), poly(T, degree=rankX-1))
  lambda <- rankX:1
  Xi <- sapply(lambda, function(l)
  scale(rnorm(N, sd=sqrt(l)), scale=FALSE))

  X <- Xi %*% t(Phi)
  
  write.matrix(X,file=paste("X_dec_", i,"_", N, ".csv", sep=""), sep= ",")

  
  # betaT<-beta(T)
  lfterm<-as.numeric((1/m)*X%*%betaT)
  alpha<-0.15
  y<-alpha+lfterm+eps
  n<-length(y)
  m<-length(T)
  
  write.matrix(y,file=paste("y_dec_", i,"_", N, ".csv", sep=""), sep= ",")
  
  Ngrid<-c(3:8)  ###grid for choosing N1
  cv<-cv.SOFR.con(Ngrid,y,X,T,constr = "dec")
  indmin<-which.min(cv)
  ###############################################
  N1 <- Ngrid[indmin] #selected N1

  
  out<-SOFR.con(N1,y,X,T,m,constr = "dec")
  # out.NULL<-SOFR.NULL(N1,y,X,T,m,constr = NULL)
  beta1t<-out$betaSOFR #constrained estimate

  yhat=out$yhat
  
  # Store fitted values in matrix
  fitted_means_matrix[i,] <- beta1t
  
  #IMSE
  IMSE_cons[i] = h*sum(t(betaT-beta1t)^2%*%W)
  # MSE
  MSE_cons[i] = mean((y-yhat)**2)
  
}
end_time= Sys.time()
tiempo_constrained = end_time - start_time
# Calculate mean and confidence intervals for each mesh point
mean_fitted_vals <- apply(fitted_means_matrix, 2, mean)
lower_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.025))
upper_ci <- apply(fitted_means_matrix, 2, function(x) quantile(x, 0.975))

# Combine results into a data frame
results_constrained <- data.frame(T=T, mean=mean_fitted_vals, lower=lower_ci, upper=upper_ci)

print(paste0('IMSE for N=',N, mean(IMSE_cons)*1000))
print(paste0('MSE for N=',N, mean(MSE_cons)*1000))
print(paste0('Standard deviation of the IMSE for N=',N, sd(IMSE_cons)))
print(paste0('Standard deviation of the MSE for N=',N, sd(MSE_cons)))
print(paste0('Times:', tiempo_constrained))
}
```





```{r, fig.width=5.5, fig.height=4.5}
#par(mfrow=c(1,2))
#
#  plot(T, betaT, col='#666E86', ylim=c(-0.05,1.5), type='l') #true coefficient function
#  lines(T,results_constrained$mean,col="#5F3108",lty=5) #unconstrained estimate
#  lines(T,results_constrained$lower,col="#B99B81",lty=3) #projection based C.I
#  lines(T,results_constrained$upper,col="#B99B81",lty=3)  #projection based C.I
#  abline(h=0, col='#780000')
#
#  plot(T,betaT, col='#666E86', ylim=c(-0.05,1.5), type='l') #true coefficient function
#  lines(T,results_unconstrained$mean,col="#5F3108",lty=5) #unconstrained estimate
#  lines(T,results_unconstrained$lower,col="#B99B81",lty=3) #projection based C.I
#  lines(T,results_unconstrained$upper,col="#B99B81",lty=3)  #projection based C.I
#  abline(h=0, col='#780000')
#  
```



```{r, fig.width=5.5, fig.height=3.5}
library(ggplot2)
library(gridExtra)
# Create a data frame with the values for T, betaT, and the results
df <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_unconstrained$mean,
                 lower = results_unconstrained$lower,
                 upper = results_unconstrained$upper)

df2 <- data.frame(T = T,
                 betaT = betaT,
                 mean = results_constrained$mean,
                 lower = results_constrained$lower,
                 upper = results_constrained$upper)

# Create the plot using ggplot


# Create a data frame with the values for T, betaT, and the results

# Create the plot using ggplot
plot1=ggplot(df, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = lower), color = "#B99B81",linetype= "dashed", size=1)+
  geom_line(aes(y = upper),color = "#B99B81", linetype="dashed", size=1)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 
# Create a data frame with the values for T, betaT, and the results


# Create the plot using ggplot
plot2=ggplot(df2, aes(x = T)) +
  geom_line(aes(y = betaT), color = "#666E86", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = mean), color = "#5F3108", linetype = "solid", 
            size = 1) +
  geom_line(aes(y = lower), color = "#B99B81",linetype= "dashed", size=1)+
  geom_line(aes(y = upper),color = "#B99B81", linetype="dashed", size=1)+
  geom_hline(yintercept = 0, color = "#780000") +
  ylim(0.05,0.3) +
  theme_bw() +
  theme(axis.line = element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    ) 

grid.arrange(plot1, plot2, nrow = 1)

#legend(0.80,95000, box.col="white", cex=1.5, c(expression(paste("MWW P-value = 1.4 * ", 10^-16))))

```





